Assessing primitives performance\\ on multi-stage execution

### 2018-05-07 paper.tex
llvm boxplot. display might change as well

    \subcaption{Taille 0}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

@@

    \subcaption{Taille 5}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

@@

    \subcaption{Taille 100}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

@@

   \subcaption{Taille 1000}
   \end{subfigure}
   \caption{GCC-Linux results}
\end{figure*}

>>>>

    \subcaption{Size 0}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

@@

    \subcaption{Size 5}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

@@

    \subcaption{Size 100}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

@@

   \subcaption{Size 1000}
   \end{subfigure}
   \caption{GCC-Linux results}
\end{figure*}

    \begin{tikzpicture}
      \begin{axis}
      [
    boxplot/draw direction
    =y,
        xtick={1,2,3,4,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        font={\tiny}
        ]
        \addplot+[
        boxplot prepared={
          median=1,
          upper quartile=1,
          lower quartile=1,
          upper whisker=1,
          lower whisker=1
        },        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=0.3162,
          upper quartile=0.3179,
          lower quartile=0.3072,
          upper whisker=0.3720,
          lower whisker=0.3022
        },        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=0.3023,
          upper quartile=0.3029,
          lower quartile=0.3006,
          upper whisker=0.3547,
          lower whisker=0.2984
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=0.8538,
          upper quartile=0.8591,
          lower quartile=0.8482,
          upper whisker=0.9920,
          lower whisker=0.7516
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=2.142,
          upper quartile=2.429,
          lower quartile=2.120,
          upper whisker=2.990,
          lower whisker=2.038
        },
        ] coordinates {};
      \end{axis}
    \end{tikzpicture}

    \subcaption{Size 0}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
    boxplot/draw direction=y,
        xtick={1,2,3,4,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        font={\tiny}
        ]
        \addplot+[
        boxplot prepared={
          median=1,
          upper quartile=1,
          lower quartile=1,
          upper whisker=1,
          lower whisker=1
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=1.261,
          upper quartile=1.270,
          lower quartile=1.227,
          upper whisker=1.282,
          lower whisker=1.205
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=1.229,
          upper quartile=1.235,
          lower quartile=1.227,
          upper whisker=1.248,
          lower whisker=1.203
        },
        ] coordinates {};
                \addplot+[
        boxplot prepared={
          median=2.832,
          upper quartile=2.847,
          lower quartile=2.814,
          upper whisker=2.875,
          lower whisker=2.706
        },
        ] coordinates {};
                \addplot+[
        boxplot prepared={
          median=7.094,
          upper quartile=7.138,
          lower quartile=7.057,
          upper whisker=7.212,
          lower whisker=6.854
        },
        ] coordinates {};
      \end{axis}
    \end{tikzpicture}

    \subcaption{Size 5}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
    boxplot/draw direction=y,
        xtick={1,2,3,4,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        font={\tiny}
        ]
        \addplot+[
        boxplot prepared={
          median=1,
          upper quartile=1,
          lower quartile=1,
          upper whisker=1,
          lower whisker=1
        },
        ] coordinates {};
         \addplot+[
        boxplot prepared={
          median=6.746,
          upper quartile=6.826,
          lower quartile=6.622,
          upper whisker=7.384,
          lower whisker=5.307
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=6.581,
          upper quartile=6.626,
          lower quartile=6.553,
          upper whisker=7.087,
          lower whisker=6.362
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=10.330,
          upper quartile=10.122,
          lower quartile=10.461,
          upper whisker=11.110,
          lower whisker=9.246
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=18.08,
          upper quartile=18.16,
          lower quartile=17.79,
          upper whisker=19.53,
          lower whisker=16.36
        },
        ] coordinates {};
      \end{axis}
    \end{tikzpicture}

    \subcaption{Size 100}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
    boxplot/draw direction
    =y,
        xtick={1,2,3,4,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        font={\tiny}
        ]
        \addplot+[
        boxplot prepared={
          median=1,
          upper quartile=1,
          lower quartile=1,
          upper whisker=1,
          lower whisker=1
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=9.485,
          upper quartile=9.521,
          lower quartile=9.314,
          upper whisker=9.720,
          lower whisker=8.831
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=9.212,
          upper quartile=9.271,
          lower quartile=9.173,
          upper whisker=9.364,
          lower whisker=8.979
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=13.48,
          upper quartile=13.61,
          lower quartile=13.33,
          upper whisker=13.70,
          lower whisker=12.81
        },
        ] coordinates {};
        \addplot+[
        boxplot prepared={
          median=26.54,
          upper quartile=26.80,
          lower quartile=26.07,
          upper whisker=27.12,
          lower whisker=25.53
        },
        ] coordinates {};
      \end{axis}
    \end{tikzpicture}

   \subcaption{Size 1000}
   \end{subfigure}
   \caption{LLVM-Mac results}
\end{figure*}
